 %==========================================以下不要动=================================================

  \pagestyle{empty}%
  \null%
  \vspace*{-6pc}%
  \begin{center}
  \begingroup
  \setlength{\parindent}{0pt}
     \begin{minipage}{0.28\linewidth}
      For office use only\\[4pt]
      \makebox[0.15\linewidth][l]{T1}\rule[-2pt]{0.85\linewidth}{0.5pt}\\[4pt]
      \makebox[0.15\linewidth][l]{T2}\rule[-2pt]{0.85\linewidth}{0.5pt}\\[4pt]
      \makebox[0.15\linewidth][l]{T3}\rule[-2pt]{0.85\linewidth}{0.5pt}\\[4pt]
      \makebox[0.15\linewidth][l]{T4}\rule[-2pt]{0.85\linewidth}{0.5pt}
     \end{minipage}%
     \begin{minipage}{0.44\linewidth}
      \centering
      Team Control Number\\[0.7pc]
      {\LARGE\textbf{\newteamnumber}}\\[1.8pc]
      Problem Chosen\\[0.7pc]
      {\Huge\textbf{\newproblemchosen}}
     \end{minipage}%
     \begin{minipage}{0.28\linewidth}
      For office use only\\[4pt]
      \makebox[0.15\linewidth][l]{F1}\rule[-2pt]{0.85\linewidth}{0.5pt}\\[4pt]
      \makebox[0.15\linewidth][l]{F2}\rule[-2pt]{0.85\linewidth}{0.5pt}\\[4pt]
      \makebox[0.15\linewidth][l]{F3}\rule[-2pt]{0.85\linewidth}{0.5pt}\\[4pt]
      \makebox[0.15\linewidth][l]{F4}\rule[-2pt]{0.85\linewidth}{0.5pt}
     \end{minipage}\par
     \vskip 8pt
  \rule{\linewidth}{0.5pt}\par
%  \vskip 8pt
  \vskip 4pt
  \textbf{{\Large\the\year}\\%
%  Mathematical Contest in Modeling (MCM/ICM) Summary Sheet}%
  MCM/ICM \\
  Summary Sheet}%
%  \par
  \endgroup
%  \vskip 8pt
 \vskip 4pt
  \normalfont \Large \ourtitle \par
%  \par
  \centering {\normalsize{\textbf{summary}}}
  \end{center}
%==========================================以上不要动=================================================

% ============================================摘要======================================================
\noindent If an alien came after 50 years, what language should it learn to understand human civilization more fully? The research findings in this article can give an answer.
In this article, we predict trends in the mainstream languages of the world today and determine the address of a new international office for a multinational corporation.
In the first stage: In the first stage, forecasting trends of global languages takes two aspects into account: the change in the total number of people in a particular language and the geographical distribution of the language. For the former, a non-equidistant gray prediction model based on historical data is established under the assumption that there is no sudden change in the number of language speakers in a region.The model gives the number of speakers of the language (ranked in the top twenty).For the latter, we consider the language speakers' geographic distribution.At this time, the influence of the regional population growth and population migration on the shift is taken into account. By applying these two models, we can obtain the change of the total number of speakers of the mainstream languages in the world(Shown in Fig.), the variations of the number of native speakers in the mainstream languages（Shown in Fig.）,languages of top ten(both native speakers and total speakers) and their ranks in fifty years（see table）.Additionally, we find none of the top ten languages of both native speakers and total speakers is replaced in fifty years and English becomes the most spoken language by the year 2045 with a total population of 1,432.163 million.As for the part of geographical distribution of language speakers,we obtain that the Arabic speakers accounts for 50.13% of the total Arabic speaker in 2048.,which indicates geographical distribution of Arabic speakers skews toword AfricaFrench also shows the same trend.
In the second stage: the establishment of language performance evaluation model (LII model) to determine the location of the new international offices. The LII model considers the specific 15 indicators of a language group in five major areas: Area, Economic strength, Language speakers, Knowledge and communication, International use. Firstly the indicator value is quantified to [0, 1], then weighted to obtain the language performance score and ranked. Analyze change of rankings of language performance score every 10 years in the future, and find that there is no change in the categories of the top 6 languages in terms of short-term or long-term. We assume that the offices are usually established in the capital of the country where the first language is the mother tongue, so six new offices are located: London, England / Paris, France / Madrid, Spain / Dammam, Saudi Arabia / Moscow, Russia / Berlin, Germany. Finally, considering the nature of the change in the global communications (geographically distant Internet connections and language barrier with powerful translation software), we think it is possible to set up an international office in each continent, that is, in addition to the United States and China , Confirming the establishment of four more new international offices.




% ============================================摘要======================================================

% ============================================下面关键字======================================================
\par
\noindent
\textbf{Key words:}Non-equal spacing GM (1,1) ,Evaluation model of language effectiveness 
