\newpage
\section{Memorandum}
\noindent
To the Chief Operating Officer of the service company:

We are honored to write you this letter. We are the team of Mathematical Modeling Mathew, will show you the trend of language development in the world in the future. at the same time, we will provide you with a plan for setting an international office. We analyzed the factors that affect population development and distribution. Through the mathematical modeling method, we get some more reliable conclusions about the tendency of language development. On this basis, we have comprehensively considered the economic, geographical advantages, education and knowledge and other factors, hoping to provide some useful suggestions for the location of your new global office.

Firstly we consider the background factor and some other factors to predict the development of the world language. The trend of language development is not only reflected in the change rule of the number of users, but also reflected in the change of geographical distribution. In order to study the changes in the number of languages in the world, we collected some useful data from the United Nations Statistics Division. However, there are data missing in some time periods. Therefore, we established a non-equidistant GM (1,1) model to predict the number of languages and forecast the number of native speakers and speakers in each of the mainstream languages in the world after 50 years.

Then, we mainly consider two factors about the geographical distribution of language: the total population of the world and immigration in the mode of population migration. Access to relevant information we have been analyzed: global population growth changes affect the distribution of language speakers, compared to different regions of the same language changes in the number of people found that geographical distribution of the mother tongue there is a shift in the center of gravity.
Immigration issues in the mode of migration mainly influence the population movements in second-language speakers.Using the un-released immigration data and the predicted increase in the number of second-language speakers in Part I, the increase in the number of speakers is rationally allocated to second-language countries. Analysis demonstrates that the number of speakers of second language languages in some countries will decrease significantly or dramatically.

Finally, we give a reasonable plan for the location of international offices. We establish the language performance evaluation model (LII), looking for objective and reasonable indicators to quantify the weighted language rank scores. Comparison of language rankings, regardless of short-term or long-term, the top six languages will not change. It is assumed that the capital of the mother tongue country corresponding to the chosen language is to establish a new office. Considering the changes in the social environment such as the Internet and the global economy, distance and lack of understanding of foreign languages are no barrier to language exchange and learning, so less than 6 new international offices can be established.

We hope our models and methods will help your company understand the trends in global languages and the rational location of new international offices will solve your company's distress. And sincerely hope that our report and its model prove useful to you, and that it may see suggestions.

Sincerely,

MCM team\#89760


